---
title: "HW 01 - Simple Linear Regression"
author: "Hannah Wang"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE)
```

### Load packages & Data

```{r load-packages, message=FALSE}
library(tidyverse)
library(readr)
library(broom)
library(knitr)
```

```{r load-data, message=FALSE}
bikeshare <- read_csv("data/bikeshare.csv")
```

## Part 1: Computations & Concepts 

### Question 1

```{r winter-only}
winter_data <- bikeshare %>%
  filter(season == 1) %>%
  mutate(temp_c = temp *41)
winter_data
```

### Question 2

```{r model}
winter_model <- lm(count ~ temp_c, data = winter_data)
tidy(winter_model, conf.int = TRUE, level = 0.95) %>%
     kable(digits = 3)
```

count = -111.038 + 222.416 * temp_c

### Question 3

We are 95% confident that the true slope of the linear relationship between number of bike rentals in the winter and temperature is between 185.990 and 248.841.


### Question 4

The width of a 90% confidence interval would be smaller than the width of the 95% confidence interval because we are now less confident that the CI captures the true slope, thus giving us a narrower range of numbers.


### Question 5

Based on the 95% confidence interval, there is a statistically significant linear relationship between temperature and number of bike rentals in the winter because the 95% confidence interval does not include a slope of 0 (no linear relationship).


### Question 6

The test statistic is 12.049, indicating a p-value of 0.00. This means that assuming the null hypothesis were true, there is a 0% chance of getting a test statistic of 12.049.

### Question 7

No, my roommate is not correct. The p-value of 0 means that assuming the null hypothesis were true, there is a 0% chance we would have gotten the results as extreme or more extreme than the output we got. Therefore, we can reject the null hypothesis that there is no linear relationship between temperature and bike rental count in the winter, in favor of the alternative hypothesis that there is a linear relationship between temperature and bike rental count in the winter.


### Question 8

```{r r-square}
glance(winter_model, winter_data)$r.squared
```
The R-squared value shows that temperature explains 44.78% of the variation in number of bikes rented in the winter.

## Part 2: Data Analysis

### Question 9

(Add code and narrative as needed.)


### Overall (Do not delete!)

You do not need to write anything for this question. We will check the following as part of your lab grade: 

- 5 pt: Documents neatly organized (.Rmd and .md files)	
- 3 pt: Narrative in full sentences and neatly organized
- 2 pt: Regular and informative commit messages	


