---
title: "HW 01 - Simple Linear Regression"
author: "Hannah Wang"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE)
```

### Load packages & Data

```{r load-packages, message=FALSE}
library(tidyverse)
library(readr)
library(broom)
library(knitr)
```

```{r load-data, message=FALSE}
bikeshare <- read_csv("data/bikeshare.csv")
```

## Part 1: Computations & Concepts 

### Question 1

```{r winter-only}
winter_data <- bikeshare %>%
  filter(season == 1) %>%
  mutate(temp_c = temp *41)
winter_data
```

### Question 2

```{r model}
winter_model <- lm(count ~ temp_c, data = winter_data)
tidy(winter_model, conf.int = TRUE, level = 0.95) %>%
     kable(digits = 3)
```

count = -111.038 + 222.416 * temp_c

### Question 3

We are 95% confident that the true slope of the linear relationship between number of bike rentals in the winter and temperature is between 185.990 and 248.841.


### Question 4

The width of a 90% confidence interval would be smaller than the width of the 95% confidence interval because we are now less confident that the CI captures the true slope, thus giving us a narrower range of numbers.


### Question 5

Based on the 95% confidence interval, there is a statistically significant linear relationship between temperature and number of bike rentals in the winter because the 95% confidence interval does not include a slope of 0 (no linear relationship).


### Question 6

The test statistic is 12.049.EXPLAIN MEANING


### Question 7

(Type your response to Question 7 here. There is no code required.)


### Question 8

```{r r-square}

```


## Part 2: Data Analysis

### Question 9

(Add code and narrative as needed.)


### Overall (Do not delete!)

You do not need to write anything for this question. We will check the following as part of your lab grade: 

- 5 pt: Documents neatly organized (.Rmd and .md files)	
- 3 pt: Narrative in full sentences and neatly organized
- 2 pt: Regular and informative commit messages	


