---
title: "HW 01 - Simple Linear Regression"
author: "Your Name"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE)
```

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(readr)
library(broom)
library(knitr)
```

```{r load-data, message=FALSE}
bikeshare <- read_csv("data/bikeshare.csv")
```

## Part 1: Computations & Concepts 

### Question 1

```{r}

```

### Question 2

```{r model}

```


```{r output-model}

```

### Question 3

(Type your response to Question 3 here. There is no code required.)


### Question 4

(Type your response to Question 4 here. There is no code required.)


### Question 5

(Type your response to Question 5 here. There is no code required.)


### Question 6

(Type your response to Question 6 here. There is no code required.)


### Question 7

(Type your response to Question 7 here. There is no code required.)


### Question 8

```{r r-square}

```


## Part 2: Data Analysis

### Question 9

(Add code and narrative as needed.)


